Assessing the potential of Jacobian-free Newton-Krylov methods for cell-centred finite volume solid mechanics

### 2025-01-16 article.tex
Update cantilever case with new loading and and abaqus results

Using Equation \ref{eq:volume_integral}, the inertia term (e.g. left-hand side term of Equation \ref{eqn:momentum_lingeom}) becomes
\begin{eqnarray} \label{eq:inertia}
	\int_{\Omega_P} \rho \frac{\partial \bb{u} }{\partial t}  d \Omega_P
%	\;&\approx&\;
%	\int_{\mathrm{\Omega}} \rho \left[ \frac{\partial \bb{u} }{\partial t}_P + (\bb{x} - \bb{x}_P) \cdot \nabla \frac{\partial \bb{u} }{\partial t}_P \right] d\mathrm{\Omega} \notag \\
	\;&\approx&\;
	\rho_P \left(\frac{\partial^2 \bb{u} }{\partial t^2}\right)_P  \Omega_P
\end{eqnarray}
Similarly, the body force term (e.g. the second term on the right-hand side of Equation \ref{eqn:momentum_lingeom}) becomes:
\begin{eqnarray}
	\int_{\Omega_P} \, \rho \, \bb{g} \,  d \Omega_P
	\;&\approx&\;
	\rho_P \, \bb{g}\,  \Omega_P
\end{eqnarray}
%where subscript $P$ indicates a quantity at the cell centre.
The discretisation of the acceleration in Equation \ref{eq:inertia} can be achieved using one of many finite difference schemes, e.g. first-order Euler, second-order backwards, or second-order Newmark-beta.
In the current work, the second-order backwards (BDF2) scheme is used:
%\begin{eqnarray}
%	 \left(\frac{\partial^2 \bb{u} }{\partial t^2}\right)_P
%	 &\approx& \frac{3\bb{v}_{t+1} - 4\bb{v}_{t} + \bb{v}_{t-1}}{2\Delta t} \notag \\
%	&\approx& \frac{3\left( \frac{3\bb{u}_{t+1} - 4\bb{u}_{t} + \bb{u}_{t-1}}{2\Delta t} \right) - 4\bb{v}_{t} + \bb{v}_{t-1}}{2\Delta t}
%\end{eqnarray}
\begin{eqnarray} \label{eq:inertia2}
	\left(\frac{\partial^2 \boldsymbol{u}_P}{\partial t^2}\right)_P
	&\approx& \frac{3\boldsymbol{v}_P^{[t+1]} - 4\boldsymbol{v}_P^{[t]} + \boldsymbol{v}_P^{[t-1]}}{2\Delta t} \notag \\
	&\approx&
	\frac{3\left( 
		\dfrac{3\boldsymbol{u}_P^{[t+1]} - 4\boldsymbol{u}_P^{[t]} + \boldsymbol{u}_P^{[t-1]}}{2\Delta t} 
		\right) 
	- 4\boldsymbol{v}_P^{[t]} + \boldsymbol{v}_P^{[t-1]}}{2\Delta t}
\end{eqnarray}
where $\Delta t$ is the time increment -- assumed constant here -- and $\bb{v} = \partial \bb{u}/\partial t$ is the velocity vector.
Superscript $[t]$ indicates the time level, with $\bb{u}_P^{[t+1]}$ corresponding to the unknown displacement at the current time step.
Consequently, the displacement and velocity at the two previous time steps must be stored, or alternatively the displacement at the previous four time steps.

\subsubsection{Surface Integrals}
The surface integrals are discretised in a similar fashion to the volume integrals, where the integrand $\bb{\phi}$ is assumed to vary locally according to a truncated Taylor series expansion about a face centroid $\bb{x}_{f_i}$:
\begin{eqnarray}
	\bb{\phi}(\bb{x})  \approx \bb{\phi}_{f_i} + (\bb{x} - \bb{x}_{f_i}) \cdot \left(\nabla \bb{\phi} \right)_{f_i}
\end{eqnarray}
where subscript $f_i$ indicates a value at the centroid of the face $f_i$.
Consequently, surface integrals about a cell $P$ can be approximated to second order accuracy as
\begin{eqnarray} \label{eq:surface_integral}
	\oint_{\Gamma_P} \bb{\phi} \, d \Gamma_P
		&=& \sum_{f_i \in \mathcal{F}_P} \int_{\Gamma_{f_i}} \bb{\phi} \,  d \Gamma_{f_i} \notag \\
		&\approx& \sum_{f_i \in \mathcal{F}_P} \int_{\Gamma_{f_i}}  \left[ \bb{\phi}_{f_i} + (\bb{x} - \bb{x}_{f_i}) \cdot \nabla \bb{\phi}_{f_i} \right] d \Gamma_{f_i} \notag \\
%		&\approx& \int_{\mathrm{\Omega}}  \bb{\phi}_P d\mathrm{\Omega}  + \int_{\mathrm{\Omega}}  (\bb{x} - \bb{x}_P) \cdot \nabla \bb{\phi}_P d\mathrm{\Omega} \notag \\
		&\approx& \sum_{f_i \in \mathcal{F}_P} \bb{\phi}_{f_i} |\bb{\Gamma}_{f_i} |
\end{eqnarray}
where $\Gamma_P$ indicates the surface of cell $P$, and $\bb{\Gamma}_{f_i}$ indicates the area vector of face $f_i$.
%$N_f$ represents the set of neighbouring cells which share a face with cell $P$,

Consequently, the surface integral term (first term on the right-hand side of Equation \ref{eqn:momentum_lingeom}), corresponding to the divergence of stress, can be discretised as
%by assuming that the stress varies linearly across the face, allowing the mid-point rule to be used:
\begin{eqnarray} \label{eq:divStressDiscret}
	\oint_{\Gamma_P} \bb{n} \cdot \bb{\sigma}  \; d\Gamma_P
	\approx 
%	\sum_{f_i \in \mathcal{F}_P^{\text{int}} \cup \mathcal{F}_P^{\text{disp}} \cup \mathcal{F}_P^{\text{symm}}} \bb{\Gamma}_{f_i} \cdot \bb{\sigma}_{f_i}
%	\sum_{f_i \in \mathcal{F}_P^{\text{non-trac}}} \bb{\Gamma}_{f_i} \cdot \bb{\sigma}_{f_i}
	\sum_{f_i \in \mathcal{F}_P^{\text{int}}} \bb{\Gamma}_{f_i} \cdot \bb{\sigma}_{f_i}
	+ \sum_{d_i \in \mathcal{F}_P^{\text{disp}}} \bb{\Gamma}_{d_i} \cdot \bb{\sigma}_{P}
	+ \sum_{s_i \in \mathcal{F}_P^{\text{symm}}} \bb{\Gamma}_{s_i} \cdot \bb{\sigma}_{s_i}
	+ \sum_{t_i \in \mathcal{F}_P^{\text{trac}}} |\bb{\Gamma}_{t_i}| \bar{\bb{T}}_{t_i}
\end{eqnarray}
where vector $\bar{\bb{T}}_{t_i}$ represents the prescribed traction on the traction boundary face $t_i$.
%For faces $f_i$ in Equation \ref{eq:divStressDiscret} that are on traction boundary faces $b_i \in \mathcal{F}_P^{\text{trac}} \subset \mathcal{F}_P$, 
%the traction $\bar{\bb{t}}_{b_i}$ is known and is directly enforced; that is, $\bb{\Gamma}_{f_i} \cdot \bb{\sigma}_{f_i} = |\bb{\Gamma}_{f_i}| \bb{n}_{f_i} \cdot \bb{\sigma}_{f_i} =  |\bb{\Gamma}_{f_i}| \bar{\bb{t}}_{b_i}$.
%subscript $f$ indicates a quantity at the centre of a cell face, and 
The stress $\bb{\sigma}_{f_i}$ at an internal face is calculated by linear interpolation from the adjacent cell centres \citep{Jasak1996}:
\begin{eqnarray} \label{eq:stressInterp}
	\bb{\sigma}_{f_i} &=& w_{f_i} \bb{\sigma}_P + (1 - w_{f_i}) \bb{\sigma}_{N_{f_i}}
\end{eqnarray}
where the interpolation ratio is defined as $w_{f_i} = (\bb{n}_{f_i} \cdot [\bb{x}_{N_{f_i}} - \bb{x}_{f_i}])/(\bb{n}_{f_i} \cdot [\bb{x}_{N_{f_i}} - \bb{x}_{P} ])$.
%For faces $f_i$ in Equation \ref{eq:divStressDiscret} that are on traction boundary faces $b_i \in \mathcal{F}_P^{\text{trac}} \subset \mathcal{F}_P$, the traction $\bar{\bb{t}}_{b_i}$ is known and is directly enforced; that is, $\bb{\Gamma}_{f_i} \cdot \bb{\sigma}_{f_i} = |\bb{\Gamma}_{f_i}| \bb{n}_{f_i} \cdot \bb{\sigma}_{f_i} =  |\bb{\Gamma}_{f_i}| \bar{\bb{t}}_{b_i}$.
%Vector $\bb{d}_{f}$ connects cell centre $P$ with cell centre $N_f$, $\bb{d}_f = \bb{x}_{N_f} - \bb{x}_P$, and $\bb{n}_{f}$ is the outward-facing unit normal to the face $f$.
Similarly, the stress $\bb{\sigma}_{s_i}$ at a symmetry boundary face is calculated as
\begin{eqnarray} \label{eq:symm}
	\bb{\sigma}_{s_i}
		&=& \frac{1}{2} \left (\bb{\sigma}_P + \bb{R}_{s_i} \cdot \bb{\sigma}_{P} \right) \notag \\
		&=& \left (\textbf{I} - \bb{n}_{s_i} \otimes \bb{n}_{s_i} \right) \cdot \bb{\sigma}_P
\end{eqnarray}
where $\bb{R}_{s_i} \cdot \bb{\sigma}_{P}$ represents the mirror reflection of $\bb{\sigma}_P$ across the symmetry boundary face $s_i$.
The reflection tensor is $\bb{R}_{s_i} = \textbf{I} - 2 \bb{n}_{s_i} \otimes \bb{n}_{s_i}$ \citep{Demirdzic2022}, with $\bb{n}_{s_i}$ indicating the unit normal of the symmetry boundary face $s_i$.
From Equation \ref{eq:symm}, it is clear that shear stresses are zero on a symmetry plane boundary face.
Note from Equation \ref{eq:divStressDiscret} that the stress on displacement boundary faces is assumed equal to the stress $\bb{\sigma}_P$ at the centroid of cell $P$.

The cell-centred stress $\bb{\sigma}_P$ is calculated as a function of the displacement gradient according to the chosen mechanical law, where the cell-centred displacement gradients are determined using a inverse-distance-weighted first-neighbours least squares method \citep{Jasak1996}:
\begin{eqnarray} \label{eq:leastSquaresGrad}
	\left(\bb{\nabla}\bb{u}\right)_P
%		&=&\sum_{f_i \in \mathcal{F}^{\text{int}}_P} \omega_{f_i}^2 \bb{G}^{-1}_P \cdot \bb{d}_{f_i} \left(\bb{u}_{N_{f_i}} - \bb{u}_P \right) \notag \\
%		&&+ \sum_{b_i \in \mathcal{F}^{\text{disp}}_P} \omega_{b_i}^2 \bb{G}^{-1}_P \cdot \bb{d}_{b_i} \left(\bb{u}_{b_i} - \bb{u}_P \right) \notag \\
%		&&+ \sum_{b_i \in \mathcal{F}^{\text{symm}}_P} \omega_{b_i}^2 \bb{G}^{-1}_P \cdot \bb{d}_{b_i}^{\text{symm}} \left(\bb{R}_{b_i} \cdot \bb{u}_P - \bb{u}_P \right)
%		&=&\sum_{f_i \in \mathcal{F}^{\text{int}}_P} \left( \nicefrac{1}{|\bb{d}_{f_i}|^2} \right) \bb{G}^{-1}_P \cdot \bb{d}_{f_i} \left(\bb{u}_{N_{f_i}} - \bb{u}_P \right) \notag \\
%		&&+ \sum_{b_i \in \mathcal{F}^{\text{disp}}_P} \left( \nicefrac{1}{|\bb{d}_{b_i}|^2} \right) \bb{G}^{-1}_P \cdot \bb{d}_{b_i} \left(\bb{u}_{b_i} - \bb{u}_P \right) \notag \\
%		&&+ \sum_{b_i \in \mathcal{F}^{\text{symm}}_P} \left( \nicefrac{1}{|\bb{d}_{b_i}^{\text{symm}}|^2} \right) \bb{G}^{-1}_P \cdot \bb{d}_{b_i}^{\text{symm}} \left(\bb{R}_{b_i} \cdot \bb{u}_P - \bb{u}_P \right) \\
		&=&\sum_{f_i \in \mathcal{F}^{\text{int}}_P} \frac{\bb{G}^{-1}_P \cdot \bb{d}_{f_i}}{\bb{d}_{f_i} \cdot \bb{d}_{f_i}}  \otimes \left(\bb{u}_{N_{f_i}} - \bb{u}_P \right) \notag \\
		&&+ \sum_{d_i \in \mathcal{F}^{\text{disp}}_P} \frac{ \bb{G}^{-1}_P \cdot \bb{d}_{d_i} }{\bb{d}_{d_i} \cdot \bb{d}_{d_i}} \otimes \left(\bb{u}_{d_i} - \bb{u}_P \right) \notag \\
		&&+ \sum_{s_i \in \mathcal{F}^{\text{symm}}_P} \frac{\bb{G}^{-1}_P \cdot \bb{d}_{s_i}}{\bb{d}_{s_i} \cdot \bb{d}_{s_i}} \otimes \left(\bb{R}_{s_i} \cdot \bb{u}_P - \bb{u}_P \right)
\end{eqnarray}
%where the least squares weights are $\omega_{f_i} = 1/|\bb{d}_{f_i}|$ and  $\omega_{b_i} = 1/|\bb{d}_{b_i}|$.
The vector $\bb{u}_{b_i}$ indicates the displacement at the centroid of boundary face ${b_i}$, while vector $\bb{d}_{d_i}$ connects the centroid of cell $P$ to the centroid of displacement boundary face $d_i$.
The quantity $\bb{R}_{s_i} \cdot \bb{u}_P$ represents the mirror reflection of $\bb{u}_P$ across the symmetry boundary face $s_i$.
% where the reflection tensor is $\bb{R}_{s_i} = \textbf{I} - 2 \bb{n}_{s_i} \otimes \bb{n}_{s_i}$ \citep{Demirdzic2022}.
The vector $\bb{d}_{s_i}$ connects the centroid $\bb{x}_P$ of cell $P$ with its mirror reflection $\bb{R}_{s_i}  \cdot \bb{x}_P$ through boundary face $s_i$.
Traction boundary faces are excluded in Equation \ref{eq:leastSquaresGrad}, as the displacement is unknown there; this is in contrast to the default approach in OpenFOAM \citep{Jasak2011}.
The $\bb{G}_P$ tensor for cell $P$ is calculated as
\begin{eqnarray}
	 \bb{G}_P &=&
%	 \sum_{{f_i} \in \mathcal{F}^{\text{int}}_P} \omega_{f_i}^2 \bb{d}_{f_i} \bb{d}_{f_i}
%	 +  \sum_{{b_i} \in \mathcal{F}^{\text{disp}}_P} \omega_{b_i}^2 \bb{d}_{b_i} \bb{d}_{b_i}
%	 +  \sum_{{b_i} \in \mathcal{F}^{\text{symm}}_P} \omega_{b_i}^2 \bb{d}_{b_i}^{\text{symm}} \bb{d}_{b_i}^{\text{symm}}
	 \sum_{{f_i} \in \mathcal{F}^{\text{int}}_P} \frac{\bb{d}_{f_i} \otimes \bb{d}_{f_i}}{\bb{d}_{f_i} \cdot \bb{d}_{f_i}}
	 +  \sum_{{d_i} \in \mathcal{F}^{\text{disp}}_P} \frac{\bb{d}_{d_i} \otimes \bb{d}_{d_i}}{\bb{d}_{d_i} \cdot \bb{d}_{d_i}}
	 +  \sum_{{s_i} \in \mathcal{F}^{\text{symm}}_P} \frac{\bb{d}_{s_i} \otimes \bb{d}_{s_i}}{\bb{d}_{s_i} \cdot \bb{d}_{s_i}}
\end{eqnarray}
where the $\bb{G}^{-1}_P \cdot \bb{d}/(\bb{d}\cdot \bb{d})$ vectors are purely a function of the mesh and can be computed once and stored.

As noted, boundary conditions are enforced through the discretised surface integrals terms at the boundaries faces. % (Equations \ref{eq:divStressDiscret} and \ref{eq:RhieChow}).
If required, the displacement $\bb{u}_{t_i}$ on a traction boundary face $t_i$ can be calculated by extrapolation from the centre of cell $P$ as
\begin{eqnarray}
	\bb{u}_{t_i} = \bb{u}_P + \bb{d}_{t_i} \cdot \left(\bb{\nabla} \bb{u} \right)_P
\end{eqnarray}
where $\bb{d}_{t_i}$ represents the vector from the centroid of cell $P$ to the centroid of the traction boundary face $t_i$.

Similarly, if required, the displacement $\bb{u}_{s_i}$ at a symmetry plane face $s_i$ is calculated using the same approach as Equation \ref{eq:symm}:
\begin{eqnarray} 
	\bb{u}_{s_i}
		&=&  \frac{1}{2} \bb{u}_P + \bb{R}_{s_i} \cdot \bb{u}_P \notag \\
		&=& \left (\textbf{I} - \bb{n}_{s_i} \otimes \bb{n}_{s_i} \right) \cdot \bb{u}_P
\end{eqnarray}

>>>>

Using Equation \ref{eq:volume_integral}, the inertia term (e.g. left-hand side term of Equation \ref{eqn:momentum_lingeom}) becomes
\begin{eqnarray} \label{eq:inertia}
	\int_{\Omega_P} \rho \frac{\partial \bb{u} }{\partial t}  d \Omega_P
%	\;&\approx&\;
%	\int_{\mathrm{\Omega}} \rho \left[ \frac{\partial \bb{u} }{\partial t}_P + (\bb{x} - \bb{x}_P) \cdot \nabla \frac{\partial \bb{u} }{\partial t}_P \right] d\mathrm{\Omega} \notag \\
	\;&\approx&\;
	\rho_P \left(\frac{\partial^2 \bb{u} }{\partial t^2}\right)_P  \Omega_P
\end{eqnarray}
Similarly, the body force term (e.g. the second term on the right-hand side of Equation \ref{eqn:momentum_lingeom}) becomes:
\begin{eqnarray}
	\int_{\Omega_P} \, \rho \, \bb{g} \,  d \Omega_P
	\;&\approx&\;
	\rho_P \, \bb{g}\,  \Omega_P
\end{eqnarray}
%where subscript $P$ indicates a quantity at the cell centre.
The discretisation of the acceleration in Equation \ref{eq:inertia} can be achieved using one of many finite difference schemes, e.g. first-order Euler, second-order backwards, or second-order Newmark-beta.
In the current work, the second-order backwards (BDF2) scheme is used:
%\begin{eqnarray}
%	 \left(\frac{\partial^2 \bb{u} }{\partial t^2}\right)_P
%	 &\approx& \frac{3\bb{v}_{t+1} - 4\bb{v}_{t} + \bb{v}_{t-1}}{2\Delta t} \notag \\
%	&\approx& \frac{3\left( \frac{3\bb{u}_{t+1} - 4\bb{u}_{t} + \bb{u}_{t-1}}{2\Delta t} \right) - 4\bb{v}_{t} + \bb{v}_{t-1}}{2\Delta t}
%\end{eqnarray}
\begin{eqnarray} \label{eq:inertia2}
	\left(\frac{\partial^2 \boldsymbol{u}_P}{\partial t^2}\right)_P
	&\approx& \frac{3\boldsymbol{v}_P^{[t+1]} - 4\boldsymbol{v}_P^{[t]} + \boldsymbol{v}_P^{[t-1]}}{2\Delta t} \notag \\
	&\approx&
	\frac{3\left( 
		\dfrac{3\boldsymbol{u}_P^{[t+1]} - 4\boldsymbol{u}_P^{[t]} + \boldsymbol{u}_P^{[t-1]}}{2\Delta t} 
		\right) 
	- 4\boldsymbol{v}_P^{[t]} + \boldsymbol{v}_P^{[t-1]}}{2\Delta t}
\end{eqnarray}
where $\Delta t$ is the time increment -- assumed constant here.
Superscript $[t]$ indicates the time level, with $\bb{u}_P^{[t+1]}$ corresponding to the unknown displacement at the current time step.
 The velocity vector $\bb{v} = \partial \bb{u}/\partial t$ at the current time step is also updated using the BDF2 scheme as
 \begin{eqnarray}
	\boldsymbol{v}_P^{[t+1]}	&\approx&
		\dfrac{3\boldsymbol{u}_P^{[t+1]} - 4\boldsymbol{u}_P^{[t]} + \boldsymbol{u}_P^{[t-1]}}{2\Delta t} 
\end{eqnarray}
Consequently, the displacement and velocity at the two previous time steps must be stored, or alternatively the displacement at the previous four time steps.

\subsubsection{Surface Integrals}
The surface integral term can be discretised as using one-point quadrature at each face $f_i$ as
%\begin{eqnarray} \label{eq:surface_integral}
%	\oint_{\Gamma_P} \bb{\phi} \, d \Gamma_P
%		&=& \sum_{f_i \in \mathcal{F}_P} \int_{\Gamma_{f_i}} \bb{\phi} \,  d \Gamma_{f_i} \notag \\
%%		&\approx& \sum_{f_i \in \mathcal{F}_P} \int_{\Gamma_{f_i}}  \left[ \bb{\phi}_{f_i} + (\bb{x} - \bb{x}_{f_i}) \cdot \nabla \bb{\phi}_{f_i} \right] d \Gamma_{f_i} \notag \\
%%		&\approx& \int_{\mathrm{\Omega}}  \bb{\phi}_P d\mathrm{\Omega}  + \int_{\mathrm{\Omega}}  (\bb{x} - \bb{x}_P) \cdot \nabla \bb{\phi}_P d\mathrm{\Omega} \notag \\
%		&\approx& \sum_{f_i \in \mathcal{F}_P} \bb{\phi}_{f_i} |\bb{\Gamma}_{f_i} |
%\end{eqnarray}
\begin{eqnarray} \label{eq:divStressDiscret}
	\oint_{\Gamma_P} \bb{n} \cdot \bb{\sigma}  \; d\Gamma_P
	&=& \sum_{f_i \in \mathcal{F}_P} \int_{\Gamma_{f_i}} \bb{n} \cdot \bb{\sigma}  \,  d \Gamma_{f_i} \notag \\
	&\approx&
%	\sum_{f_i \in \mathcal{F}_P^{\text{int}} \cup \mathcal{F}_P^{\text{disp}} \cup \mathcal{F}_P^{\text{symm}}} \bb{\Gamma}_{f_i} \cdot \bb{\sigma}_{f_i}
%	\sum_{f_i \in \mathcal{F}_P^{\text{non-trac}}} \bb{\Gamma}_{f_i} \cdot \bb{\sigma}_{f_i}
	\sum_{f_i \in \mathcal{F}_P^{\text{int}}} \bb{\Gamma}_{f_i} \cdot \bb{\sigma}_{f_i}
	+ \sum_{d_i \in \mathcal{F}_P^{\text{disp}}} \bb{\Gamma}_{d_i} \cdot \bb{\sigma}_{P}
	+ \sum_{s_i \in \mathcal{F}_P^{\text{symm}}} \bb{\Gamma}_{s_i} \cdot \bb{\sigma}_{s_i}
	+ \sum_{t_i \in \mathcal{F}_P^{\text{trac}}} |\bb{\Gamma}_{t_i}| \bar{\bb{T}}_{t_i}
\end{eqnarray}
where $\Gamma_P$ indicates the surface of cell $P$, and $\bb{\Gamma}_{f_i}$ indicates the area vector of face $f_i$, and vector $\bar{\bb{T}}_{t_i}$ represents the prescribed traction on the traction boundary face $t_i$.
%where $\Gamma_P$ indicates the surface of cell $P$, and $\bb{\Gamma}_{f_i}$ indicates the area vector of face $f_i$.

It is noted that the displacement is assumed to vary linearly within each cell; hence, the displacement gradient and stress are constant within each cell.
In the current work, a unique definition of stress $\bb{\sigma}_{f_i}$ at each cell face $f_i$ is given as a weighted-averaged of values in the two cells ($\bb{\sigma}_P $, $\bb{\sigma}_{N_{f_i}}$) straddling the face \citep{Jasak1996}:
%The stress $\bb{\sigma}_{f_i}$ at an internal face is calculated by linear interpolation from the adjacent cell centres \citep{Jasak1996}:
\begin{eqnarray} \label{eq:stressInterp}
	\bb{\sigma}_{f_i} &=& w_{f_i} \bb{\sigma}_P + (1 - w_{f_i}) \bb{\sigma}_{N_{f_i}}
\end{eqnarray}
%where $\bb{\sigma}_{f_i}$ is the stress at an interface face $f_i$, 
where the interpolation weight is defined as $w_{f_i} = (\bb{n}_{f_i} \cdot [\bb{x}_{N_{f_i}} - \bb{x}_{f_i}])/(\bb{n}_{f_i} \cdot [\bb{x}_{N_{f_i}} - \bb{x}_{P} ])$; however, achieving second-order accuracy of the displacement field is independent of the value of the weights, and, for example, $w_{f_i} = \nicefrac{1}{2}$ would also be sufficient.
Similarly, the stress $\bb{\sigma}_{s_i}$ at a symmetry boundary face is calculated as
\begin{eqnarray} \label{eq:symm}
	\bb{\sigma}_{s_i}
		&=& \frac{1}{2} \left (\bb{\sigma}_P + \bb{R}_{s_i} \cdot \bb{\sigma}_{P} \right) \notag \\
		&=& \left (\textbf{I} - \bb{n}_{s_i} \otimes \bb{n}_{s_i} \right) \cdot \bb{\sigma}_P
\end{eqnarray}
where $\bb{R}_{s_i} \cdot \bb{\sigma}_{P}$ represents the mirror reflection of $\bb{\sigma}_P$ across the symmetry boundary face $s_i$.
The reflection tensor is $\bb{R}_{s_i} = \textbf{I} - 2 \bb{n}_{s_i} \otimes \bb{n}_{s_i}$ \citep{Demirdzic2022}, with $\bb{n}_{s_i}$ indicating the unit normal of the symmetry boundary face $s_i$.
From Equation \ref{eq:symm}, it is clear that shear stresses are zero on a symmetry plane boundary face.
Note from Equation \ref{eq:divStressDiscret} that the stress on displacement boundary faces is assumed to be equal to the stress $\bb{\sigma}_P$ at the centroid of cell $P$.

%The surface integrals are discretised in a similar fashion to the volume integrals, where the integrand $\bb{\phi}$ is assumed to vary locally according to a truncated Taylor series expansion about a face centroid $\bb{x}_{f_i}$:
%\begin{eqnarray}
%	\bb{\phi}(\bb{x})  \approx \bb{\phi}_{f_i} + (\bb{x} - \bb{x}_{f_i}) \cdot \left(\nabla \bb{\phi} \right)_{f_i}
%\end{eqnarray}
%where subscript $f_i$ indicates a value at the centroid of the face $f_i$.
%Consequently, surface integrals about a cell $P$ can be approximated to second-order accuracy as
%\begin{eqnarray} \label{eq:surface_integral}
%	\oint_{\Gamma_P} \bb{\phi} \, d \Gamma_P
%		&=& \sum_{f_i \in \mathcal{F}_P} \int_{\Gamma_{f_i}} \bb{\phi} \,  d \Gamma_{f_i} \notag \\
%		&\approx& \sum_{f_i \in \mathcal{F}_P} \int_{\Gamma_{f_i}}  \left[ \bb{\phi}_{f_i} + (\bb{x} - \bb{x}_{f_i}) \cdot \nabla \bb{\phi}_{f_i} \right] d \Gamma_{f_i} \notag \\
%%		&\approx& \int_{\mathrm{\Omega}}  \bb{\phi}_P d\mathrm{\Omega}  + \int_{\mathrm{\Omega}}  (\bb{x} - \bb{x}_P) \cdot \nabla \bb{\phi}_P d\mathrm{\Omega} \notag \\
%		&\approx& \sum_{f_i \in \mathcal{F}_P} \bb{\phi}_{f_i} |\bb{\Gamma}_{f_i} |
%\end{eqnarray}
%where $\Gamma_P$ indicates the surface of cell $P$, and $\bb{\Gamma}_{f_i}$ indicates the area vector of face $f_i$.
%$N_f$ represents the set of neighbouring cells which share a face with cell $P$,

%Consequently, by assuming $\bb{\phi}$ represents $\bb{n} \cdot \bb{\sigma}$ in Equation \ref{eq:surface_integral}, the surface integral term (first term on the right-hand side of Equation \ref{eqn:momentum_lingeom}), corresponding to the divergence of stress, can be discretised as
%%by assuming that the stress varies linearly across the face, allowing the mid-point rule to be used:
%\begin{eqnarray} \label{eq:divStressDiscret}
%	\oint_{\Gamma_P} \bb{n} \cdot \bb{\sigma}  \; d\Gamma_P
%	\approx 
%%	\sum_{f_i \in \mathcal{F}_P^{\text{int}} \cup \mathcal{F}_P^{\text{disp}} \cup \mathcal{F}_P^{\text{symm}}} \bb{\Gamma}_{f_i} \cdot \bb{\sigma}_{f_i}
%%	\sum_{f_i \in \mathcal{F}_P^{\text{non-trac}}} \bb{\Gamma}_{f_i} \cdot \bb{\sigma}_{f_i}
%	\sum_{f_i \in \mathcal{F}_P^{\text{int}}} \bb{\Gamma}_{f_i} \cdot \bb{\sigma}_{f_i}
%	+ \sum_{d_i \in \mathcal{F}_P^{\text{disp}}} \bb{\Gamma}_{d_i} \cdot \bb{\sigma}_{P}
%	+ \sum_{s_i \in \mathcal{F}_P^{\text{symm}}} \bb{\Gamma}_{s_i} \cdot \bb{\sigma}_{s_i}
%	+ \sum_{t_i \in \mathcal{F}_P^{\text{trac}}} |\bb{\Gamma}_{t_i}| \bar{\bb{T}}_{t_i}
%\end{eqnarray}
%where vector $\bar{\bb{T}}_{t_i}$ represents the prescribed traction on the traction boundary face $t_i$.
%For faces $f_i$ in Equation \ref{eq:divStressDiscret} that are on traction boundary faces $b_i \in \mathcal{F}_P^{\text{trac}} \subset \mathcal{F}_P$, 
%the traction $\bar{\bb{t}}_{b_i}$ is known and is directly enforced; that is, $\bb{\Gamma}_{f_i} \cdot \bb{\sigma}_{f_i} = |\bb{\Gamma}_{f_i}| \bb{n}_{f_i} \cdot \bb{\sigma}_{f_i} =  |\bb{\Gamma}_{f_i}| \bar{\bb{t}}_{b_i}$.
%subscript $f$ indicates a quantity at the centre of a cell face, and 
%The stress $\bb{\sigma}_{f_i}$ at an internal face is calculated by linear interpolation from the adjacent cell centres \citep{Jasak1996}:
%\begin{eqnarray} \label{eq:stressInterp}
%	\bb{\sigma}_{f_i} &=& w_{f_i} \bb{\sigma}_P + (1 - w_{f_i}) \bb{\sigma}_{N_{f_i}}
%\end{eqnarray}
%where the interpolation ratio is defined as $w_{f_i} = (\bb{n}_{f_i} \cdot [\bb{x}_{N_{f_i}} - \bb{x}_{f_i}])/(\bb{n}_{f_i} \cdot [\bb{x}_{N_{f_i}} - \bb{x}_{P} ])$; however, using a value of $\nicefrac{1}{2}$ would also be sufficient to achieve second-order accuracy of the displacement field.
%For faces $f_i$ in Equation \ref{eq:divStressDiscret} that are on traction boundary faces $b_i \in \mathcal{F}_P^{\text{trac}} \subset \mathcal{F}_P$, the traction $\bar{\bb{t}}_{b_i}$ is known and is directly enforced; that is, $\bb{\Gamma}_{f_i} \cdot \bb{\sigma}_{f_i} = |\bb{\Gamma}_{f_i}| \bb{n}_{f_i} \cdot \bb{\sigma}_{f_i} =  |\bb{\Gamma}_{f_i}| \bar{\bb{t}}_{b_i}$.
%Vector $\bb{d}_{f}$ connects cell centre $P$ with cell centre $N_f$, $\bb{d}_f = \bb{x}_{N_f} - \bb{x}_P$, and $\bb{n}_{f}$ is the outward-facing unit normal to the face $f$.
%Similarly, the stress $\bb{\sigma}_{s_i}$ at a symmetry boundary face is calculated as
%\begin{eqnarray} \label{eq:symm}
%	\bb{\sigma}_{s_i}
%		&=& \frac{1}{2} \left (\bb{\sigma}_P + \bb{R}_{s_i} \cdot \bb{\sigma}_{P} \right) \notag \\
%		&=& \left (\textbf{I} - \bb{n}_{s_i} \otimes \bb{n}_{s_i} \right) \cdot \bb{\sigma}_P
%\end{eqnarray}
%where $\bb{R}_{s_i} \cdot \bb{\sigma}_{P}$ represents the mirror reflection of $\bb{\sigma}_P$ across the symmetry boundary face $s_i$.
%The reflection tensor is $\bb{R}_{s_i} = \textbf{I} - 2 \bb{n}_{s_i} \otimes \bb{n}_{s_i}$ \citep{Demirdzic2022}, with $\bb{n}_{s_i}$ indicating the unit normal of the symmetry boundary face $s_i$.
%From Equation \ref{eq:symm}, it is clear that shear stresses are zero on a symmetry plane boundary face.
%Note from Equation \ref{eq:divStressDiscret} that the stress on displacement boundary faces is assumed equal to the stress $\bb{\sigma}_P$ at the centroid of cell $P$.

The cell-centred stress $\bb{\sigma}_P$ is calculated as a function of the displacement gradient according to the chosen mechanical law, where the cell-centred displacement gradients are determined using an inverse-distance-weighted first-neighbours least squares method \citep{Jasak1996},
\begin{eqnarray} \label{eq:leastSquaresGrad}
	\left(\bb{\nabla}\bb{u}\right)_P
%		&=&\sum_{f_i \in \mathcal{F}^{\text{int}}_P} \omega_{f_i}^2 \bb{G}^{-1}_P \cdot \bb{d}_{f_i} \left(\bb{u}_{N_{f_i}} - \bb{u}_P \right) \notag \\
%		&&+ \sum_{b_i \in \mathcal{F}^{\text{disp}}_P} \omega_{b_i}^2 \bb{G}^{-1}_P \cdot \bb{d}_{b_i} \left(\bb{u}_{b_i} - \bb{u}_P \right) \notag \\
%		&&+ \sum_{b_i \in \mathcal{F}^{\text{symm}}_P} \omega_{b_i}^2 \bb{G}^{-1}_P \cdot \bb{d}_{b_i}^{\text{symm}} \left(\bb{R}_{b_i} \cdot \bb{u}_P - \bb{u}_P \right)
%		&=&\sum_{f_i \in \mathcal{F}^{\text{int}}_P} \left( \nicefrac{1}{|\bb{d}_{f_i}|^2} \right) \bb{G}^{-1}_P \cdot \bb{d}_{f_i} \left(\bb{u}_{N_{f_i}} - \bb{u}_P \right) \notag \\
%		&&+ \sum_{b_i \in \mathcal{F}^{\text{disp}}_P} \left( \nicefrac{1}{|\bb{d}_{b_i}|^2} \right) \bb{G}^{-1}_P \cdot \bb{d}_{b_i} \left(\bb{u}_{b_i} - \bb{u}_P \right) \notag \\
%		&&+ \sum_{b_i \in \mathcal{F}^{\text{symm}}_P} \left( \nicefrac{1}{|\bb{d}_{b_i}^{\text{symm}}|^2} \right) \bb{G}^{-1}_P \cdot \bb{d}_{b_i}^{\text{symm}} \left(\bb{R}_{b_i} \cdot \bb{u}_P - \bb{u}_P \right) \\
